Do investors in clean energy ETFs herd?

### 2025-03-24 alt_energy_herding.qmd
small changes

tribble(
  ~ " ", ~ "Mean", ~ "St.dev", ~ "Skewness", ~ "Kurtosis",
  "CSAD",  "0.0062", "0.0034", "1.5598", "7.9355",
  "Absolute CSAD",  "0.0094", "0.0107", "3.3175", "23.8725"
) |> 
  flextable_pdf() |> 
  align(align = "left", j = 1, part = "all") |>
  hline_bottom(part = "footer", border = fp_border(color = "black", style = "solid", width = 1)) |> 
  autofit(add_w = 0.6)

@@

$$
CSAD_t = \gamma_0 + \gamma_1 R_{m,t} + \gamma_2 R_{m,t}^2 + \epsilon_t,
$$ {#eq-herding}

>>>>

tribble(
  ~ " ", ~ "Mean", ~ "St.dev", ~ "Skewness", ~ "Kurtosis",
  "CSAD",  "0.0062", "0.0034", "1.5598", "7.9355",
  "Absolute CSAR",  "0.0094", "0.0107", "3.3175", "23.8725"
) |> 
  flextable_pdf() |> 
  align(align = "left", j = 1, part = "all") |>
  hline_bottom(part = "footer", border = fp_border(color = "black", style = "solid", width = 1)) |> 
  autofit(add_w = 0.6)

@@

$$
CSAD_t = \gamma_0 + \gamma_1 |R_{m,t}| + \gamma_2 R_{m,t}^2 + \epsilon_t,
$$ {#eq-herding}

### 2025-03-24 alt_energy_herding.tex
small changes

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.46in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Absolute\ CSAD}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0094}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0107}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.23in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{3.3175}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{23.8725}}}} \\

@@

\begin{equation}\phantomsection\label{eq-herding}{
CSAD_t = \gamma_0 + \gamma_1 R_{m,t} + \gamma_2 R_{m,t}^2 + \epsilon_t,
}\end{equation}

>>>>

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.46in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Absolute\ CSAR}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0094}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0107}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.23in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{3.3175}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{23.8725}}}} \\

@@

\begin{equation}\phantomsection\label{eq-herding}{
CSAD_t = \gamma_0 + \gamma_1 |R_{m,t}| + \gamma_2 R_{m,t}^2 + \epsilon_t,
}\end{equation}
